Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-11 longSC.tex
You and Ante's comments

\section{Introduction}
\label{sec:intro}
The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP). 
%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
%The matter produced in a heavy-ion collision exhibits strong collective radial expansion. Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
The matter produced in a heavy-ion collision exhibits strong collective radial expansion. 
Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into short direction of the almond,
that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf,Aad:2014eoa}. The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

@@

\noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angle brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

@@

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}. It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}. 
The first theoretical studies of SC observables can be found in Refs.~\cite{Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.

@@

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we obtain the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from the $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
%Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions. 
%NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, though the model does not describe them quantitatively.

>>>>

\section{Introduction}
\label{sec:intro}
The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP). 
%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
%The matter produced in a heavy-ion collision exhibits strong collective radial expansion. Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
The matter produced in a heavy-ion collision exhibits strong collective radial expansion. 
Geometrical anisotropy of the almond shaped overlap region of the colliding nuclei causes larger pressure gradients into shorter direction of the almond,
that results in anisotropic transverse flow in the momentum space through interactions of the matter constituents.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} is also observed at LHC energies~\cite{Aamodt:2010pa,ALICE:2011ab,Abelev:2014pua,Adam:2016izf,ATLAS:2011ah,ATLAS:2012at,Aad:2013xma,Aad:2014eoa,Chatrchyan:2012wg,Chatrchyan:2012ta,Chatrchyan:2012xq}. The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

@@

\noindent where $E$, $\bold{p}$, $p_{\mathrm{T}}$, $\varphi$ and $\eta$ are the particle's energy, momentum, transverse momentum, azimuthal angle and pseudorapidity, respectively, and $\Psi_n$ is the azimuthal angle of the symmetry plane of the $n^{\mathrm{th}}$-order harmonic. Harmonic $v_n$ can be calculated as $v_{n} = \langle{\cos[n(\varphi - \Psi_n)]}\rangle$, where the angular brackets denote an average over all particles in all events.
%Anisotropic flow in Heavy-ion collision can be written as an azimuthal ($\phi$) asymmetry of the single-particle distribution~\cite{Luzum:2011mm}:
%\begin{equation}
%\label{defVn}
%P(\varphi)=\frac{1}{2\pi}\sum_{n=-\infty}^{+\infty}V_n e^{-in\varphi},
%\end{equation}
%where $V_n$ is the (complex) anisotropic flow coefficient in the $n$th harmonic.
%One usually uses the notation $v_n$ for the magnitude: $v_n\equiv|V_n|$.
The anisotropic flow in heavy-ion collisions is typically understood as the hydrodynamic response of the produced matter to spatial deformations of the initial energy density profile~\cite{Floerchinger:2013tya}.
This profile fluctuates event-by-event due to fluctuating positions of the constituents inside the colliding nuclei, which implies that $v_n$ also fluctuates~\cite{Miller:2003kd,Alver:2006wh}.
The recognition of the importance of flow fluctuations led to the discovery of triangular and higher flow harmonics~\cite{Alver:2010gr,ALICE:2011ab} as well as to the correlations between different $v_{n}$ harmonics~\cite{Niemi:2012aj,Aad:2014fla}.
%The measurements by the ATLAS Collaboration~\cite{} show that higher order harmonics are sensitive to the $\eta/s$~\cite{Luzum:2012wu}.
The higher order harmonics are expected to be sensitive to fluctuations in the initial conditions and to the magnitude of $\eta/s$~\cite{Alver:2010dn,Luzum:2012wu}, while $v_{n}$ correlations have the potential to discriminate between these two respective contributions~\cite{Niemi:2012aj}.
%And the $v_{n}$ distributions carry detailed information about the initial energy density profile~\cite{Renk:2014jja,Yan:2014nsa}.

@@

The ALICE measurements~\cite{ALICE:2016kpq} have revealed that fluctuations of $v_2$ and $v_3$ are anti-correlated, while fluctuations of $v_2$ and $v_4$ are correlated for all centralities~\cite{ALICE:2016kpq}. It was found that the details of the centrality dependence differ in the fluctuation-dominated (most central) and the geometry-dominated (mid-central) regimes~\cite{ALICE:2016kpq}. The observed centrality dependence of SC(4,2) cannot be captured by models with constant $\eta/s$, indicating that the temperature dependence of $\eta/s$ plays an important role. These results were also used to discriminate between different parameterizations of initial conditions. It was demonstrated that in the fluctuation-dominated regime (central collisions), MC-Glauber initial conditions with binary collision weights are favored over wounded nucleon weights~\cite{ALICE:2016kpq}. 
The first theoretical studies of SC observables can be found in Refs.~\cite{Zhou:2015eya,Giacalone:2016afq,Qian:2016pau,Gardim:2016nrr,Zhu:2016puf,Ke:2016jrd}.

@@

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we present the results as a function of the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals; this decreases large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) as a function of minimum $p_{\rm T}$ cuts are shown in Figs.~\ref{fig:Figure_2}a and \ref{fig:Figure_2}c.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
The centrality dependence is stronger with higher $p_{\rm T, min}$ cuts, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
The NSC(3,2) and NSC(4,2) observables with different $p_{\rm T, min}$ are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the individual flow harmonics $\left<v_n\right>$. 
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate increase of anti-correlation with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
The NSC(4,2) observable shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from the $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

The comparison to the VISH2+1 calculation~\cite{Zhu:2016puf} is shown in Fig.~\ref{fig:Figure_4}.  All calculations with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial conditions) fail to capture the centrality dependence of the SC($m$,$n$) observables of all orders, shown in the left panels in Fig.~\ref{fig:Figure_4}.
Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial conditions describes the data better than the ones with other initial conditions for all SC($m$,$n$) observables measured, but it cannot describe the data quantitively for most of the centrality ranges.
%Similar to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in the model calculations in Fig.~\ref{fig:Figure_4} is opposite to that in data in 5--10\% central collisions. 
%NSC(3,2) and NSC(4,3) are not very sensitive to the initial conditions or $\eta/s$ parameterization used in the model, and are not described quantitatively.
The comparisons of the measured NSC(3,2) and NSC(4,3) to VISH2+1 model calculations suggest that they are not very sensitive to the initial conditions or $\eta/s$ parameterization, but it is clear that this model does not describe them quantitatively.
